Towards user-friendliness in proof assistants: automated strategies \textbf{via} algebraic effects and handlers

### 2021-06-26 paper/main.tex
add paper
spelling remove duplicated a

\paragraph{Contributions} The project is a work-in-progress, but this paper
makes three important contributions that pave the way for the full implementation:
\begin{enumerate}
\item a specification of a user interface for automated proofs based on
  algebraic effects and handlers that permits user-defined effects for proof
  strategies, and also user-defined handlers for existing effects (Section \ref{intro-witch});
\item a short technical account of the effort required to implement such a
  user interface for proof assistants via a a minimal prototype in Agda that
  validates the feasibility of such system  (Section \ref{tech-details}).
\end{enumerate}

>>>>

\paragraph{Contributions} The project is a work-in-progress, but this paper
makes three important contributions that pave the way for the full implementation:
\begin{enumerate}
\item a specification of a user interface for automated proofs based on
  algebraic effects and handlers that permits user-defined effects for proof
  strategies, and also user-defined handlers for existing effects (Section \ref{intro-witch});
\item a short technical account of the effort required to implement such a
  user interface for proof assistants via a minimal prototype in Agda that
  validates the feasibility of such system  (Section \ref{tech-details}).
\end{enumerate}
